\begin{fboxed}
  \begin{enumerate}[leftmargin=1em]
    \item \label{ass:risk-groups}\textbf{Risk Groups:}
    Major demographic groups are stratified by risk of HIV acquisition.
    \begin{enumerate}
      \item \label{ass:risk-groups-no}\textbf{No:} $\G = 1$;
      Major demographic groups are homogeneous in risk of HIV acquisition.
      \item \label{ass:risk-groups-yes}\textbf{Yes:} $\G > 1$;
      Heterogeneity in risk of HIV acquisition within major demographic groups is considered.
    \end{enumerate}
    \item \label{ass:attr-death}\textbf{Attributable Death:}
    Deaths attributable to HIV affect the group sizes $\bm{x}$.
    \begin{enumerate}
      \item \textbf{No:} $\bm{\phi} = 0$;
      Death attributable to HIV is not considered.
      \item \textbf{Yes:} $\bm{\phi} > 0$;
      Attributable death is considered.
    \end{enumerate}
    \item \label{ass:rebalance}\textbf{Risk Group Re-Balancing:}
    Dynamic rate parameters attempt to re-balance the groups.
    \\(due to changes from attributable death)
    \begin{enumerate}
      \item \textbf{No:} $\bm{\x} = f(t)$;
      Group proportions $\bm{\x}$ are not re-balanced.
      \item \textbf{Yes via $\bm{\e}$:} $\bm{\e} = f(\bm{\x})$;
      Group proportions $\bm{\x}$ are re-balanced using
      a dynamic distribution of the entering population $\bm{\e}$.
      \item \textbf{Yes via $\zeta$:} $\zeta = f(\bm{\x})$;
      Group proportions $\bm{\x}$ are re-balanced using
      dynamic rates of turnover among risk groups $\zeta$.
    \end{enumerate}
    \item \label{ass:turnover}\textbf{Turnover:}
    Individuals may move between risk groups.
    \begin{enumerate}
      \item \textbf{No:} $\zeta = 0$;
      Individuals do not move between risk groups.
      \item \textbf{Constant:} $\zeta = C$;
      Individuals move between risk groups at a constant rate.
      \item \textbf{Dynamic:} $\zeta = f(\bm{\x})$;
      Individuals move between risk groups in response to the current model state.
    \end{enumerate}
    \item \label{ass:pop-growth}\textbf{Population Growth:}
    Increase in the total $\N$ over time.
    \begin{enumerate}
      \item \textbf{No:} $\nu = \mu$;
      Population size $\N$ is constant.
      \item \textbf{Yes:} $\nu > \mu$;
      Population size $\N$ increases, at some constant or data-driven rate.
    \end{enumerate}
  \end{enumerate}
\end{fboxed}
